Finding the Most Suitable Code Clone Refactoring Techniques by Mapping Clone Context

### 2019-12-06 cefp/paper.tex
Clone relation

\section{Context Analysis of Clones}\label{chap:contextsetup}
We define the following aspects of the clone as its context:
\begin{enumerate}
  \item \textbf{Relation:} The relation of clone instances in a clone class among each other through inheritance.
  \item \textbf{Location:} Where a clone instance occurs in the code.
  \item \textbf{Contents:} The statements/declarations of a clone instance.
\end{enumerate}
We define categories for each of these aspects and enable CloneRefactor to determine the categories of clones.

@@

Fig.~\ref{fig:clonecontext} shows an abstract representation of clone classes and clone instances. The relation of clones through inheritance is determined for each clone class. The location and contents of clones are determined for each clone instance.

@@

Fontana et al.~\cite{fontana2015duplicated} describe measurements on 50 open source projects on the relation of clone instances to each other. To do this, they first define several categories for the relation between clone instances in object-oriented languages. These categories are as follows:
\begin{enumerate}
  \item \textbf{Same Method}: All instances of the clone class are in the same method.
  \item \textbf{Same Class}: All instances of the clone class are in the same class.
  \item \textbf{Superclass}: All instances of the clone class are in a class that are child or parent of each other.
  \item \textbf{Sibling Class}: All instances of the clone class have the same parent class.
    \item \textbf{Ancestor Class}: All instances of the clone class are superclasses except for the direct superclass.
  \item \textbf{First Cousin Class}: All instances of the clone class have the same grandparent class.
\item \textbf{Same Hierarchy Class}: All instances of the clone class belong to the same inheritance hierarchy, but do not belong to any of the other categories.
\item \textbf{Same External Superclass}: All instances of the clone class have the same superclass, but this superclass is not included in the project but part of a library.
\item \textbf{Unrelated class}: There is at least one instance in the clone class that is not in the same hierarchy.
\end{enumerate}

We added the following categories, to gain more information about clones and reduce the number of unrelated clones:

@@

\begin{figure}[H]
  \centering
    \includegraphics[width=0.6\columnwidth]{img/Relation}
      \caption{Abstract figure displaying relations of clone classes. Arrows represent superclass relations.}
  \label{fig:clonerelation}
\end{figure}

@@

When CloneRefactor applies automated refactorings, it uses this inheritance relation to see where it must place the refactored code. We explain this for each relation category over the following sections.

@@

Cloned classes with a \textit{No Direct Superclass} relation mark the opportunity for creating a superclass abstraction and placing the extracted method there. For clone classes with a \textit{No Indirect Superclass} relation, CloneRefactor creates such an abstraction for the ancestor that does not have a parent. Clone classes with a \textit{External Superclass} or \textit{External Ancestor} relation obstruct the possibility of creating a superclass abstraction. In such a case, CloneRefactor creates an interface abstraction to make their relation explicit.

>>>>

\section{Context Analysis of Clones}\label{chap:contextsetup}
The context of a clone determines how it should be refactored~\cite{fowler2018refactoring}. Based on current literature \cite{fontana2012duplicated, fontana2015duplicated}, we define the following aspects of a clone as its context:
\begin{enumerate}
  \item \textbf{Relation:} The relation of clone instances in a clone class among each other through inheritance.
  \item \textbf{Location:} Where a clone instance occurs in the code.
  \item \textbf{Contents:} The statements/declarations of a clone instance.
\end{enumerate}

This is shown schematically in Figure~\ref{fig:clonecontext}.
%We define categories for each of these aspects and determine the categories of clones.

@@

%Fig.~\ref{fig:clonecontext} shows an abstract representation of clone classes and clone instances. The relation of clones through inheritance is determined for each clone class. The location and contents of clones are determined for each clone instance.

@@

Fontana et al.~\cite{fontana2015duplicated} describe measurements on 50 open source projects on the relation between clone instances in a clone class. To do this, they first define several categories to argue about such relations. These categories are as follows:
\begin{enumerate}
  \item \textbf{Same Method}: All instances of the clone class are in the same method.
  \item \textbf{Same Class}: All instances of the clone class are in the same class.
  \item \textbf{Superclass}: All instances of the clone class are in a class that are child or parent of each other.
  \item \textbf{Sibling Class}: All instances of the clone class have the same parent class.
    \item \textbf{Ancestor Class}: All instances of the clone class are superclasses except for the direct superclass.
  \item \textbf{First Cousin Class}: All instances of the clone class have the same grandparent class.
\item \textbf{Same Hierarchy Class}: All instances of the clone class belong to the same inheritance hierarchy, but do not belong to any of the other categories.
\item \textbf{Same External Superclass}: All instances of the clone class have the same superclass, but this superclass is not included in the project but part of a library.
\item \textbf{Unrelated class}: There is at least one instance in the clone class that is not in the same hierarchy.
\end{enumerate}

We added the following categories, to gain more information about clones and be able to suggest a more fine-grained refactoring opportunity:

@@

\begin{figure}[H]
  \centering
    \includegraphics[width=0.6\columnwidth]{img/Relation}
      \caption{Abstract figure displaying some relations of clone classes. Arrows represent superclass relations.}
  \label{fig:clonerelation}
\end{figure}

@@

%When CloneRefactor applies automated refactorings, it uses this inheritance relation to see where it must place the refactored code. We explain this for each relation category over the following sections.

@@

Cloned classes with a \textit{No Direct Superclass} relation mark the opportunity for creating a superclass abstraction and placing the extracted method there. For clone classes with a \textit{No Indirect Superclass} relation, it is possible to create such an abstraction for the ancestor that does not have a parent. Clone classes with a \textit{External Superclass} or \textit{External Ancestor} relation obstruct the possibility of creating a superclass abstraction. In such a case, it is possible to create an interface abstraction to make their relation explicit.
